\documentclass[char]{LRSguildcamp1}
\begin{document}
\name{\cArchitect{}}

\bigquote{``Architecture should speak of its time and place, but yearn for timelessness.''}{- Frank Gehry}

Your name is \cArchitect{\intro} and you are an architect. You are 40 years old and your professional life is near prefect. You are the head architect at a firm headquartered in \pCityArchitect{} that entertains offers from across the world.  You are secure enough that you can pick and choose your clients: As Ayn Rand observed, ''I don't build in order to have clients. I have clients in order to build.'' Your designs balance the functional needs with a sense of elegance and purpose. From childhood, you have always found a sense of beauty and satisfaction in the clean, ordered lines of a blueprint and the mathematics that underpins the system. Your skill at your chosen craft has always received praise and admiration from others, except from the one place you secretly want it the most--your family. 

Recently, you have a renewed interest in building something that will command respect from even them -- and the perfect chance just came along. The local hero and villain teams in \pCityArchitect{} have just put in bids for your company's services in building a new headquarters. Your firm only has the capacity to take on one project of this size. Your firm has three principal holders who control the actions of the company. Your two colleagues both have different opinions. One wants to work for the heroes and the other the villains. You suspect both have been equally incentivized. You are the deciding vote on which contract to take. You need to make a call at the end of your trip to cast your vote. You are looking foward to seeing what your siblings will be offering you.  

Your family is super in the most literal sense. Your \cGrandma{\parent}, \cGrandma{}, is a renowned \cGrandma{\villain}, art thief, and occasional high profile celebrity kidnapper. \cGrandma{\Theyhave} held the city of \pCityGrandma{} for years. Your two siblings have always cast a shadow over your life. Being the middle child was supposed to be challenging, but your situation borders on ridiculous. Your older \cOldest{\sibling}, \cOldest{} has always followed \cGrandma{} down the path of villainy and was the golden child through your younger years. Just when \cOldest{} moves out, your younger \cYoungest{\sibling}, \cYoungest{} is born and takes the lion share of attention. \cYoungest{\They}, as the baby of the family always get off scot-free, even becoming a \cYoungest{\hero} -- which \cGrandma{} brushes it off as nothing. 

The one shining part of your home life as a child was your \cGS{\parent}, \cGS{}. \cGS{} always supported your interests, although admittedly not sharing them. During take your child to work days, \cGS{} would plan \cGS{\their} heists around the latest building that had caught your interests and take you to the most restricted places. \cGS{} would laugh over \cGS{\their} shoulder, saying that nothing was off limits for \cGS{\their} kid. Your favorite adventure was when \cGS{\they} took you to eat donuts on top of the Statute of Liberty and remarked on how men try to live forever.  ``You know, \cArchitect{}, some \cGS{\humans} like me pull these big jobs so we will be remembered, but looking at you, I see another way. You are going to build something magnificent, something people will remember and use for generations. I'm so proud of you.'' Your \cGS{\parent} died a month later of a heart attack, not long after \cYoungest{} was born. That day is emblazoned into your memory, and is the reason you chose to base your firm in \pCityArchitect{}.

You yourself do have powers, but where other people seem to orbit their lives around them -- you view yours merely as a useful tool. Your power is canceling out other superhumans' powers. This sometimes comes in useful when taking contracts with super clients. You do not use your power daily, but it is a tool to be deployed when needed.

\cGrandma{} has told you countless times that you are wasting your true talent. Despite what \cGrandma{} contends, you have a deep-seated suspicion that \cGrandma{\theyare} afraid of your power, because it makes \cGrandma{\them} feel weak. You have not received a hug from your \cGrandma{\parent} since your power manifested. It's something you don't like to examine too closely but since having children of your own, \cTeen{}, your oldest, and \cTween{}, your youngest, you have tried to demonstrate your love by providing them a stable life. This has met with mixed success, but overall you have a loving relationship with your children.  There is one secret, however, you have been keeping from them about their \cAS{\parent}, \cAS{}.

You were married to \cAS{}, who you met at college while studying architecture. \cAS{} was a breath of fresh air; while \cAS{\they} had powers, \cAS{\they} still chose to purse a more typical degree and seemed wonderfully down to earth. \cAS{} even managed to get along with your older \cOldest{\sibling}, \cOldest{} and \cOldest{\their} partner \cOS{}. You got married and had two kids. You thought everything was going all right and you were working hard to build a stable life for your new family. After \cTween{} was born, \cAS{} started to see things differently and \cAS{\they} explained how \cAS{\they} felt confined and ignored. \cAS{\They} wanted to get some space.  \cAS{\They} took your children, \cTeen{} who was 6 and \cTween{} who was only 1. They moved into \cOS{}'s place in \pCityO{}. \cAS{} sent divorce papers soon after.

You went to confront \cAS{} about taking the children without any formal agreement. You went to \cOS{}'s house. You asked \cAS{} to come have a conversation with you about what was happening in your relationship. You left your two kids and \cGrad{} with \cGrad{}'s nanny. You ended up in a indoor green space inside a shopping center. While in the midst of the argument, something went terribly wrong.

You heard the sound of breaking concrete. \cAS{} ran to go investigate, and you followed. A young \cJuggernaut{\hero}-in-training, \cJuggernaut{}, came barreling through the wall near you and passed within arms' reach. You were in shock and unable to react. \cJuggernaut{} sped forward and plowed through a support beam and another shop at the far end of the green space. Part of the roof caved in and smashed into \cAS{}. \cAS{\They} died on impact. 

You could not believe your eyes. There was nothing you could have done.  You never had the special training those who go to the super high school receive. This was not your fault, except there was a small voice in your head that whispered your powers could have stopped this if you had only reached out. \cJuggernaut{} continued \cJuggernaut{\their} path of destruction leaving you with the tableau of the mangled body of the person who was once the love of your life. You ran. 

After several hours, you returned to the scene to find \cOS{} and the police coordinating off the scene. You learn that no one had seen you at the scene and you did not correct them. Your children were returned to you that very day and you began funeral arrangements. You are not proud of your behavior, either your freezing or silence, but what good would it do to tell? You have told no one. You have thought about it, but as more time passes, it always seemed it would do more harm than good. Over the next 13 years, you have built a secure life style for your children and have tried to spare them the drama and danger that follows your super family. 

\cGrandma{} has called the family together for an reunion. \cGrandma{\They} told you mostly \cGrandma{\they} wanted to see \cGrandma{\their} grandchildren and bemoaned how you never visit. Although uncertain, you suspect that the announcement might be about \cGrandma{\their} retirement, as \cGrandma{\they} recently had a fall.


\begin{itemz}[Goals]
	\item Decide which competing bid for a building an HQ for either the Hero Team or the Villain Team. Get as much money and concession from your sibling as possible.
	
	\item Convince \cTween{} to go a non-super high school. You would rather your children do not become super heroes. \cTween{} going to the same non-super school, \pNormalSchool{} as \cTeen{}, is a good start. 
	
	\item Convince \cTeen{} to use \cTeen{\their} talent for design to move into a STEM field and not Supering.
	
	\item Keep a positive relationship with your children
	
	\item Improve your relationship with your \cGrandma{\parent}. You really just want a hug, but your powers make \cGrandma{\them} feel uncomfortable.
	\end{itemz}

\begin{itemz}[Notes]
	\item 
\end{itemz}

\begin{contacts}
	\contact{\cGrandma{}} This is your \cGrandma{\parent} who is a renowned villain, art thief, and occasional high profile celebrity kidnapper. \cGrandma{\Theyare} older and already past the age of retirement for most villains.
	
	\contact{\cOldest{}} This is your older \cOldest{\sibling} and you lived in \cOldest{\their} shadow growing up. \cOldest{\They} were good friends with your spouse before \cAS{\their} death. \cOldest{} is a villain. 
	
	\contact{\cOS{}} This is \cOldest{}'s spouse. You have a friendly relationship with \cOS{\them}. As a hero, you truthfully you don't know how their relationship works, but they seem happy if dysfunctional.  \cOldest{} and \cOS{} are constantly fighting over who is in charge of \pCityO{}.  Over the last 20 years, \pCityO{} has changed hands so many times you have lost count and decided that it does not really matter who it is. 
	
	\contact{\cGrad{}} \cGrad{} is \cOldest{} and \cOS{}'s only child and just graduated from college. 
	
	\contact{\cYoungest{}} \cYoungest{} is your younger \cYoungest{\sibling} and a \cYoungest{\hero}. You think \cYoungest{they} have always been your \cGrandma{\parent}'s favorite who can do no wrong. 
	
	\contact{\cYS{}} \cYS{} is a \cYS{\hero} and apparently been dating \cYoungest{} for a while. You have not met them before. 
	
	\contact{\cTeen{}} Your oldest child who is a high school student at the \pNormalSchool{}. \cTeen{\They} have a flair for building super tech, including heat and freeze rays. In fact, \cTeen{} got in trouble for freezing a substitute teacher and subsequently lost the rights to said heat and freeze ray two weeks ago. \cTeen{} is currently on suspension from school. \cTeen{} needs some more boundaries. You would strongly prefer if both your children took on non-super careers.
	
	\contact{\cTween{}} Your youngest child is about to decide what high school to enter. \cTween{} must decide tonight! \cTween{} loves a good mystery and is always collecting information on something. This has led to some trouble at school in 6th grade, for example when \cTween{\they} wrongly accused two teachers of hitting the principal's car. That being said, \cTween{\they} was right the third time about the culprit. You would strongly prefer if both your children took on non-super careers.
\end{contacts}

\end{document}
