\documentclass[char]{LRSguildcamp1}
\begin{document}
\name{\cYS{}}

You are \cYS{\intro}, just \cYS{}. 

People often ask how it happened. You were born in a normal family, one without any supers. If you had never come into contact with any supers you might never have known that your power could significantly augment other peoples powers. Foolishly, your parents celebrated your powers since that was a way to rise in the world. You would have an easy life, they said. They were happy to give you away to the first hero that came calling. 

You will always curse your elementary school science fair to the end of your days. One of the experiments toppled into the other, causing the building to catch fire. The superhero of the city, \cEther{}, swooped in to save the children, but there were too many and the fire was spreading fast. By the time they had gotten to you, they were exhausted and barely flying. When they reached out to you, all you felt was a burst of white light behind your eyes as you passed out. 

They took you to the scientists of the superhero community, who poked and prodded and made you do different experiments with different superpowered beings until they knew the ins and outs of all your abilities. You were taken in and sponsored by \cEther{\them}. \cEther{\they} paid for your lessons, did your paperwork and took care of you in exchange for power-ups. \cEther{\they}  paid for your combat training so you would be able to survive in super-fights as an ally instead of just being a weak point. As a result, you can beat most supers in the community without their powers and many of them even when they do use their powers. 

\cEther{\they} sent you to school with the rest of the powered children, but you weren't very social in \pSuperSchool{} because your minders never liked you socializing too much. They said that you had to focus on your studies to make it worth the resources they had invested in you. You had a hard time making friends. You do remember \cYoungest{} though, the universally-liked one who was friends with everyone. \cYoungest{} was someone that you would have been scared to talk to, afraid of being rejected by this popular person.  

Even after you graduated, you were still subject to the whims of the higher-ups in the League. You owed them your position, other heroes in your cohort would say. Once, while interning in \pCityO{}, you made  mistake. It was small one, you'd later tell yourself that you'd gotten used to listening and following the whims of other, but the effect was enormous. You were city-sitting with  \cJuggernaut{}, who was another one of those popular jocks and a child of another superhero on the Council. \cJuggernaut{} kept egging you on to charge \cJuggernaut{\them} up more, just a little more. They started by cajoling, playing the don't you want to be cool like me card, and then moved on to threatening make your life in the League even harder than it was already. You know you should have just ignored them, consequences be damned, but something they said got to you. You don't even really remember what it was. Maybe there was even a little voice that told you \cJuggernaut{} deserved to lose control and get in bit of trouble. You had become very good at being precise with you charges by then. So you supercharged them.  

This ended up causing the Chicago Incident. It haunts you to this day that you caused the deaths of so many innocents. 

The League used you and fed you to the wolves. After the press thoroughly dragged your former superhero name through the mud, you were benched permanently and forbidden from using your powers without consent from the Council. You were stripped of your superhero status, although your sponsor was able to get you a position in the League Archives. That's where you realized it was possible to leave. That's also where you discovered your true talents. 

You spent three years there accumulating knowledge about the League. Based on the knowledge you acquired, you were able to gather information on the Council members who damned you and you were able to exploit a tiny loophole in the contract to leave with minimum fuss.  Leaving was surprisingly painless, a quick fee, throwing your old name to the wind... was it really that each to throw away the past decade?  

You went dark and found your niche with other former superheroes that veered off track. Taking jobs from some petty criminals helped you pay the bills for your apartment and put food on the table. The apartment was as broken as you were and the food would barely have sustained a dog, but you never felt freer. 

You continued to use some of the skills you'd developed in the Archive. After a year of lying low, you started writing about the underbelly of the City, delving deep into the histories of the place and the psychologies of the people who populated it. You made your name, a fake name, writing the beat in that area. Sometimes you sold information, there are things that you aren't proud of having done. 

It didn't last long. six years after leaving the League, the editor of the local newspaper recognized you. You'd tried only to communicate with the papers though a messenger or the Internet but somehow this person put two and two together and found the not the reporter fake name you, but the superhero you used to be. It was a situation that was of mutual profit. Superhero scandals sold the most papers because they were rare. This offered you the chance to expose those hypocritical heroes on the council, because it was mutual profit. All you had to give them was every dirty detail you could get your hands on. 

You entered the community again, looking very much different, taking a different name \cYS{\MYsupername}. Certainly, if anyone cared the check the archives they would know that you were the same person. But the people you used to work with had moved on and not many people would recognize you anyhow amongst the younger ones.  

After systematically taking down the old guard on the Council with scandal after scandal over the last 3 years, you eventually were left with fewer and fewer names on your list. You pondered the rest of the people on the Council, most of them were simply complicit in the Chicago Incident cover-up. \cYoungest{} was one of the few left, the spotless one, the face of the brand. You didn't believe that there were any spotless people left. 
 
You got yourself signed up for the emotional support group run by \cYoungest{}. Somehow, it wasn't what you expected. You found yourself opening up with \cYoungest{}, telling \cYoungest{} more and more about yourself even though you were supposed to be finding out more about them. You don't know what \cYoungest{} sees in you, but \cYoungest{} is one of the few super people who does not feel like they're trying to use you. \cYoungest{} makes you feel safe, made you believe just a little that there might be good in the world. These feelings are confusing. You're not sure if you love \cYoungest{} or you just love the sense that you've won the game?

Since the article on \cYoungest{} has gone caput, you need to find another feature to fill its place and your Editor has been on your back for a while. Just another week you tell her, and hope that you will be able to get something at this dinner. However, you have to keep this on the down-low because who know how \cYoungest{} will react? You now know that \cYoungest{} hates reporters as does the rest of the family, probably. 

You are very very nervous about meeting \cYoungest{} family, especially \cOS{}. You know it was \cOS{} city that you wrecked, but you were too scared then to apologise then. It's been 13 years, and you wonder if \cOS{} will be able to forgive you, or what you will have to do to make things right. You weren't close with \cOS{} so you aren't very sure how \cOS{\they} will react when seeing you again. 

There i۪s the great opportunity to get to know some of the biggest names in the villain business, \cGrandma{} is a legend. You would also love to be able to interview to interview \cOldest{} and \cOS{} one of the most famous Villain-Hero couples. Either way there's a story in this family your Editor will pay you quite bit for. 


\begin{itemz}[Goals]
	\item Figure out how you feel about \cYoungest{}. 
	\item Get a piece written on \cGrandma{} or \cOldest{} and \cOS{}. 
	\item Collect necessary information without being discovered, publish as many interesting stories as possible.
	\item Try to make it up to \cOS{}, with money or any other means.
	\item Try to get to know the family. 
	\item Do not get discovered by the family as a reporter. 

\end{itemz}

\begin{itemz}[Notes]
	\item You're not sure how to handle the situation with \cOS{}, but you've been keeping it in so lonng that it will feel cathartic when you finally talk to them. 
	
		
\end{itemz}

\begin{contacts}
	\contact{\cOldest{}} A middling \cOldest{\villain} in the community. Is often seen by the press as more of a political animal than a real menace. Their torrid romance still sells papers. 
	\contact{\cOS{}} The hero who briefly mentored you and \cJuggernaut{}. In a torrid romance with \cOldest{}. 
	\contact{\cGrandma{}} \cYoungest{} mother,  \cGrandma{\villain} extraordinaire.  
	\contact{\cArchitect{}} \cYoungest{} \cYoungest{\sibling}, an architect. 
	\contact{\cYoungest{}} Your lover and a hero. 
	\contact{\cGrad{}}  \cOldest{} and \cOS{} child. Has powers of invisibility.  
	\contact{\cTeen{}} \cArchitect{}'s older child, a technical wizard.
	\contact{\cTween{}} \cArchitect{}'s younger child, has super-hearing.  
	
\end{contacts}

\end{document}
