\documentclass[blue]{LRSguildcamp1}
\begin{document}
\name{\ChicagoIncident{}}

The regulations regarding in-training Super Heroes are very stringent in what is and is not permissible. At one time, in-training Super Heroes were permitted to go on patrols on their own, but this is not longer the case. 

The reasons stems back to the incident thirteen years ago in the \pCityO{}. \cYS{} and --redacted--, in-training Super Heroes, from \pSuperSchool{}, the Super high school, were doing on site training in \pCityO{}. Their mentor \cYS{} went on rounds and left them alone. A small group of villains appeared and started a bank robbery. Goaded on by \cAS{}, the two in-training super heroes went to assist in the bank robbery. --Redacted-- acquitted themselves well, but the circumstances changed quickly. \cAS{} recklessly used \cAS{their} power to over charge --redacted-- in a very populated urban center of \pCityo{}.  The property and human life damage was extensive. Property damaged registered in the millions. Dozens of innocent by-standers were injured and one of well-known Hero, \cAS{}, was killed while off duty. Subsequent investigation found \cYS{} to be at fault for unauthorized power use and \cOS{} was found negligent in supervision. The resulting affects became a one term pre-in-service training all members of \pSuperSchool{} must attend before their internships and supervising Heroes must be present at all times when in-training heroes utilize their powers.

%OS is mentoring J + YS - super hero in training
% OS goes out heroing
% J + YS start dealing with some villians. J has YS super charge them
% A comes to see AS at the O household
% A + AS go to have adult conversation, Grad follows
% J rampages breaks into area
% A doesn't stop J, AS sides, Grad sees
% A runs, Grad runs
% OS returns, sees wrecakge, A returns -- but not one suspects A was there
% J tells police "what happened" + parent connections
% A gets kids back and plans funneral and returns to new york
% YS is blackened by council, goes V








\end{document}
