\documentclass[blue]{LRSguildcamp1}
\begin{document}
\name{\bChicagoIncident{}}

The regulations regarding in-training superheroes are very stringent in what is and is not permissible. At one time, in-training superheroes were permitted to go on patrols on their own, but this is not longer the case. Thirteen years ago in the \pCityO{}, \cYSOldName{} and \cJuggernaut{}, in-training superheroes from \pSuperSchool{}, were doing on site training in \pCityO{}. Their mentor \cOS{\MYsupername} went on rounds and left them alone. 

A small group of villains appeared and started a bank robbery. Goaded on by \cYSOldName{}, the two in-training super heroes went to assist in fighting the robbers. \cJuggernaut{} acquitted himself well, but the circumstances changed quickly. Surge recklessly used \cYS{\their} power to over charge \cJuggernaut{} in a populated urban center of \pCityO{}. The property and casualties were extensive. Property damage registered in the millions. Dozens of innocent bystanders were injured and one well-known hero, \cAS{\MYsupername}, was killed while off duty. Subsequent investigations found that \cYSOldName{} was at fault for unauthorized, reckless power use and \cOS{\MYsupername} was found negligent in supervision. Afterward, any training member of the \cHeroLeague{\intro} must complete a class on safety before having access to internships and mentorships with other heroes. 


%OS is mentoring J + YS - super hero in training
% OS goes out heroing
% J + YS start dealing with some villians. J has YS super charge them
% A comes to see AS at the O household
% A + AS go to have adult conversation, Grad follows
% J rampages breaks into area
% A doesn't stop J, AS sides, Grad sees
% A runs, Grad runs
% OS returns, sees wrecakge, A returns -- but not one suspects A was there
% J tells police "what happened" + parent connections
% A gets kids back and plans funneral and returns to new york
% YS is blackened by council, goes V








\end{document}
