\documentclass[green]{LRSguildcamp1}
\begin{document}
\name{\gGMHandbook{}}

If a player comes to you from instructions behind \iArtworkThree{}, if they are not a grandkid, tell them they don't see anything interesting.
If they are a grandkid, ask them for the four digit code.  If they say 1962, tell them it says: 
``Steal the \iBagofHolding{} that belongs to \cOS{} and bring it to me. The first person who presents it to me will win the grand prize!''
If they don't already know, tell them they are tased and cannot use electronics for two minutes.
%{\em If you are not one of \cGrandma{}'s grandchildren, this is completely uninteresting.}
\\
\cChrisHemsworth{\intro} instructions:\\

``Once their eyes adjust to the darkness in the lair, they will see that you have stuck \cChrisHemsworth{\intro} in a block of steel and left him in the room. You have taped a sign to \cChrisHemsworth{} that says Try Me. Hopefully your grandchildren are smart enough to figure that one out. You like him much more than than the last one, some Downey fellow,  who complained to much and didn't appreciate your charms. 

\cChrisHemsworth{} will ask each of your grandchildren the riddle, which is what has cities, but no houses; forests, but no trees; and water, but no fish? The answer is a map, which should lead them to \iArtworkThree{}. Perhaps it's a bit oblique, but that is what \cChrisHemsworth{} is there for. 

Once they've figured out the riddle to \cChrisHemsworth{}'s satisfaction, they may leave but must wait 10 minutes before proceeding to the next step.''
\end{document}
