\documentclass[green]{LRSguildcamp1}
\begin{document}
\name{\gGrandmasChallenge{}}

Need \$50,000.  

Enter Grandma's lair by going through a series of bullets. Instructions next to the entrance of the lair, NPC bound and gagged on the other side of the bullet field.  - This is to test their physical fitness
can be done with bulletproof cape
can be done by using climbing kit to swing over the bullets
something can be tinkered with one of the artwork frames to make a shield
if hit, will be a leg wound. 
10 minutes 
 
Riddle me this - Mind test
Chris will give you the riddle to help figure out which art piece and the key for the next part. 
 
10 mins between each part. 

Use what?s on the face of the artwork to solve. (Some people may choose to steal) - prove you can steal.   Steal mechanic- roll d6 and you can steal. Use code to figure out message hidden on face of artwork. Next step in message.  

All Artworks will have a hidden label on back with 
Name of Artwork: 
Artist: 
Year Made: 
Tinkering Number if applicable
Message if applicable

In the case of Grandma's Art, the Artist Name will be a very suspicious anagram, possibly hinted at with Chris, the Year made will be a relevant Year and the Name of the Artwork will make specific reference to Grandma's past.


Steal OS's Bag of Holding and Present to Grandma. This is the final step and how to eliminate the others, since there's only one bag of holding. Straightforward stealing and then have to get to Grandma and roleplay that. OS?s bag is not tinkerable.  




\end{document}
