\documentclass[green]{LRSguildcamp1}
\begin{document}
\name{\gGrandmasChallenge{}}

This is your reminder for the lovely challenge you've set our for your Grandchildren. You're a super villainess, but not so cruel as to make the challenge impossible. After all this is just a practice run to see which has the most requisite side-kick abilities. You do hope that they will exceed your expectations. 

1. Enter \pGrandmasLair{} by going through a \sBullets{}. Who can resist some nice bullets? This is good practice for them, because they will be running a lot of errands for you. The bullets are of course, non-lethal. 
%can be done with bulletproof cape
%can be done by using climbing kit to swing over the bullets
%something can be tinkered with one of the artwork frames to make a shield
%if hit, will be a leg wound. 

%5 minutes for their eyes to adjust to the dark lair

2. Once their eyes adjust to the darkness in the lair, they will see that you have bound and gagged \cChrisHemsworth{} and left him in the room. You have taped a sign to \cChrisHemsworth{} that says Try Me. Hopefully your grandchildren are smart enough to figure that one out. Dear Chris has volunteered to stay and be tied up in exchange for some of your signature brisket that'll be served at the dinner. You like him much more than than the last one, some Downey fellow,  who complained to much and didn't appreciate your charms. 

%Once Chris is freed the first time, he may either reset himself or if more than one player is in the room he can give the riddle to both. 

3. Chris will ask each of your grandchildren the riddle, which is what has cities, but no houses; forests, but no trees; and water, but no fish? The answer is a map, which should lead them to \iArtworkThree{}. Perhaps its a bit oblique, but that is what \cChrisHemsworth{} is there for. 

Once they've figured out the riddle to \cChrisHemsworth{} satisfaction, they may leave but must wait 10 minutes before proceeding to the next step. 

4. Next they must use the number of colored keys in \iArtworkThree{} to get the four digit combination to unlock the glass case that \iArtworkThree{} is housed in. There are 1,962 colored keys in the installation, so you've made the combination lock 1962. Quite a memorable year.  

%If literally no one has figured this out 1 hour before the end of the game, \cChrisHemsworth{} will break out of the lair and assist the characters in some way. 

5. If they then are able to roll a d6 and remove the art from its case, they would find that the final step is to steal \cOS{} \iBagofHolding{} and present it to you in a grand manner. You find yourself thinking quite fondly of your grandchildren, the future is looking up. 


\end{document}
