\documentclass[green]{LRSguildcamp1}
\begin{document}
\name{\gPR{}}
Call HQ and let their PR department handle it
This option is only available to people who have declared for a team (this is an incentive to pick a side if you have a story to tell)
You have minimal control over how the story breaks. (Modifier always benefits the Team (H/V) breaking the news.)

Internet
This option is only available to Tween.
Anyone can approach Tween and get them to post something to the internet under a pseudonym. (It is role play to figure out who is the internet leak). Tween has ultimate control over the spin (Tween picks the modifier.)

Newspaper
This option is available only to YS
Anyone can approach YS and get them to submit an article to their publisher. (It is role play to figure out who the journalist is.) YS has ultimate control over the spin (YS picks the modifier.)

The PR Mechanic (public green sheet?)
To break a story you do the following:
Write down the story on a piece of in game paper that exists for this purpose. Possibly white sheets labeled "Press Release".
Write down your name as the person breaking the story (may not lie).
Roll a d6 (or whatever die we are using for mechanics), Add any modifiers you have/want (see below). Record this number as "Spin"


Deposit the press release in the envelope attached to the sign for your HQ (if you have one). If you aren't part of a team, you can't break a story unless you have another way to get information out.  [we then give Tween and YS abilities that allow them to deposit press releases in innocuous signs that say things like "A computer" or "A wall phone", or even just "Sign I" and "Sign N" or something]
Tell a GM you have sent off a press release.
The GM then goes and gets the story from the packet, reviews the spin number, modifies a "Public Opinion" number that represents general public opinion on Heroes, and publicly posts the story on a "news board". Tween and YS can publish anonymously, or list the name of the person who gave them the story instead of using their own name if they want. 
Heroes want to bring that number up, Villains want to bring that number down.  On the "You are a hero" blue sheet you add a goal that says "keep Public Opinion of the Hero league high," and to the villains that they want to lower that number.  And possibly specify that whichever hero wants to break the real story about the coverup of the Chicago incident values that above Public opinion of the hero league.
Modifiers to PR Mechanic:
Values that can be rolled on the die range from 1-6. With modifiers, you could technically get values as low as -2 or as high as 8; we'd list a full chart with all of the options and their impact. We publicly list the impact of each die value (i.e.: a value of 2 on the die is worth -2 points to the PO number.)
Submitting a story to your HQ automatically provides a modifier that benefits that group's goal (Hero league is +1 to die roll, Villain compact is -1 to die roll).
Submitting a story through Tween or YS gives them the option to +/- 1 from the die roll at their discretion.

If one of your adult superhero or supervillain relatives endorses you, that counts as worth \$20,000.  Only one endorsement adds value.
Public opinion of heroes and villains will move by 1 in the endorser's preferred direction.

\end{document}
