\documentclass[green]{LRSguildcamp1}
\begin{document}
\name{\gTinkering{}}

So you want to build a new item! As a tinker there are a variety of things you can build, you can really let your imagination take you to different places. 

In order to build a new item, first go to GM and ask how much the item will cost to make. The GM may also tell you the limitations of this item if built. You may not be able build some items. The items you used are destroyed once your item is made. You can only build out of items marked as tinkerable.

Bring two or more tinkerable items whose combined price equals or exceeds the established price for the item you wish to build to the GM. 
The GM will then make an item card for you. Spend 30 seconds role playing the making of the item in an impressive and flashy way. This is an uninterruptable action. When you are finished roll a d6.  If you roll a 1-2, your item short circuits and fills the room with smoke. You may try to rebuild the item after 10 minutes. 

If you have one tinkerable item and enough cash then you can still build the new item, but it will take more time as you need to order the missing item. Tell the GM what you want to make and give the GM your one tinkerable item and money. Wait 10 minutes then make item as stated above. (This simulates waiting for the other item to be delivered.) 

For instance, you might try to build a Freeze Ray, valued \$30,000, with one item valued at \$10,000 and another item valued at \$20,000. You could also build this item with three items all valued \$10,000 and so forth. You could also build this item with an item valued at \$5,000 and \$25,000 of cash. 

% Items in game will be labeled as Tinkerable. 
%At least a few items known ahead of game: Freeze ray for $30K?
%Super sewing machine: maybe $20K
%Automatic lock picker: $40K
\end{document}
